Closing the empirical cycle

### 2022-11-09 action_letter.Rmd
Add supplemental tables

```{r}
library(revise)
man <- revise::read_manuscript("manuscript/manuscript.Rmd")
```

@@

Thank you for considering my manuscript for publication in _`r rmarkdown::metadata$journal`_.
I appreciate the thorough and critical comments you solicited,
which helped strengthen the argumentation, clarify the structure, and add nuance.
I have made a good-faith effort to address all comments as thoroughly as possible.
All changes are explained below, and the difference between the current version and previous one can be seen at <https://github.com/cjvanlissa/rigorous_exploration/compare/d8ba218..48d2b17>.
I hope that you will find the quality of the work to be sufficiently improved.

@@

<!-- ` get_revision(man, "test")` -->

@@

@@

@@

Note that a recent perspective on the bioecological theory emphasizes that distal factors like culture are often enacted proximally by close others.
This claim might help explain why we found that distal factors were relatively less important predictors;
if distal effects are largely mediated by proximal actors,
their importance might be attenuated by conditioning on proximal effects.

@@

We respectfully believe that this may have been an oversight,
as this information was already provided. As per the submission guidelines, some specific details had been masked for review, which may have caused the oversight. To address this comment, we have unmasked these details in the revision:

@@

`r get_revision(man, "waves")`

@@

`r get_revision(man, "dutch")`

@@

As requested, we have addressed this comment by providing more detail and an illustrative example, please refer to our response to Reviewer 1.

@@

@@

@@

If we understand correctly, this statement requires no further action.

@@

While we are willing to adjust the language as requested,
we do disagree that the statement does not fit the findings.
First of all, note that the top 10 is an arbitrary criterion;
placing the 'cutoff' for important predictors in different places lends more versus less support to the statement.

Variable importance follows an approximately exponential distribution,
which means that the first variables are more important than later ones.
At least the first two most important variables are both individual characteristics.
If we interpret the variable importance like a scree plot (which is also an exponential distribution), then we observe a drop after the first 6 variables, and another drop after the 12th.
Of the first 6, only one relates to the adolescent-reported *relationship with* parents, not *parenting behaviors*. The rest of these top 6 are all individual differences.
Of variables 7-12, two relate to characteristics of the parents - mother's age and interparental conflict. Again, not parenting behavior. The rest of variables in this group relates to individual differences and adolescents' conflict behaviors.
Variables 16 and 25 are the first parenting behaviors.
I think that's a surprisingly low score.

REF

@@

We thank the Reviewer for pointing this out. We have clarified this, as requested.

@@

One potential reason is that the performance of these fit statistics has been validated in the context of confirmatory factor analysis, and their performance is less well understood for complex models.
This may affect the CFI more than, e.g., RMSEA, because CFI compares the fit of the theoretical model to a null model that may be inappropriate for longitudinal data.
For this reason, it has been suggested to rely more on RMSEA for confirmatory studies (in this case, the growth model part of the analyses is confirmatory), and on CFI for exploratory purposes [@rigdonCFIRMSEAComparison1996].
In line with the above, other research, which we now cite in the revision, has also found the RMSEA to be better at detecting misspecifications of growth curve models than CFI [@leiteDetectingGrowthShape2011]:

`r get_revision(man, "cfi")`

@@

We apologize; the Repository was still set to private at time of submission. This was intended to guarantee anonymous review. For this revision, it has been made public. The links should now work.

@@

To address this comment, and a comment by another Reviewer, we tested for differences on demographic characteristics and the dependent variable between participants with missing and complete data. We now mention this in the revised manuscript:

`r get_revision(man, "missing")`

@@

We appreciate the Reviewer's kind words, but don't give us too much credit - PCA is the oldest dimension reduction technique (invented in 1901), and the main reason we use it here is because it makes fewer assumptions about the measurement model than, e.g., CFA.

We do appreciate the excellent suggestion of providing a specific example to help readers understand this approach. To address this comment, we have thus made the following changes:

1. We added the requested illustrative example, using neuroticism. We could use any scale, but as Neuroticism later turns out to be the most important predictor, it seems a suitable candidate.
2. We have attempted to clarify our description of the dimension reduction procedure
3. We have added further statistics that, hopefully, give the reader a better sense of whether the use of these principal components is defensible. Specifically, we no longer just provide the explained variance by each first component - but we also standardize this explained variance by the number of items in the scale to see how much more variance the first component explains than expected by chance. We see that, across all scales, the first component explains between 1.6 - 17.46 times more variance than expected by chance.

We hope this addresses the comment.

@@

`r get_revision(man, "homoscedastic")`

@@

`r get_revision(man, "homogeneity")`

@@

We have simply rewritten this step in an attempt to address this comment. It now reads:

`r get_revision(man, "stepiii")`

@@

`r get_revision(man, "fullygrown")`

@@

`r get_revision(man, "semforests")`

@@

`r get_revision(man, "predictions")`

@@

`r get_revision(man, "examplenonlinear")`

@@

`r get_revision(man, "limitations")`

@@

Thank you for this suggestion; we agree that many people would be interested in such an overview. One major caution is that such post-hoc analyses should not be over-interpreted; they are in no way a substitute for the (much more flexible) machine learning models. Still, if people e.g. want to take guidance from our list of important predictors, having an overview of univariate linear effects might be useful to help plan follow-up studies.

To address this comment, we have added the following paragraph and an additional Supplemental Table:

`r get_revision(man, "posthoc")`

@@

`r get_revision(man, "errata")`

@@

`r get_revision(man, "includepersonality")`

@@

This is correct; at the time of submission, the repository on GitHub was still set to private. For the revision, this has been resolved.

@@

We apologize. The manuscript only has 42 pages; pages 43-65 are copies of the online supplemental materials (which are supposed to be accessed via the broken links, which have now been fixed). For the sake of blind review, we also submitted copies of these tables through the submission portal, but it evidently cannot correctly present these materials. The tables will not be part of the paper in this form.

@@

@@

We understand why the Reviewer expects the analysis to include model tuning and cross-validation; these are standard procedures in machine learning.
However, these methods do not (yet?) exist for SEM-forests.
This is because there is no single error metric for SEM-forests that can be optimized.
For standard random forests, this error metric is the root mean squared error (difference between predicted and observed values for all cases).
The "outcome" of each regression tree in the SEM-forest is an entire SEM-model, for which there is no clear-cut case-specific error metric.
It is important to note, however, that unlike other techniques, random forests typically achieve competitive performance even with default settings [@probstHyperparametersTuningStrategies2019].
Thus, even when a model isn't tuned - or cannot be tuned, as is the case here - it should perform well.
Although we did attempt to explain these points in the previous version of the manuscript,
we have attempted to address this comment by further emphasizing this in the Revision:

`r get_revision(man, "limitations")`

@@

We thank the Reviewer for this excellent suggestion, and now provide this figure

@@

@@

@@

In principle, this is possible.
In practice, it is not, for the following reason:
1) Computing univariate partial dependence profiles is already so computationally expensive that I cannot repeat it without additional funding
2) There is no way of determining what bivariate interactions might be important in SEM-forests analysis (because there is no applicable analogy for Friedman's H statistic)
3) So one would have to examine all bivariate interactions by hand, for all model parameters. This comes down to interpreting 84*84*3 = 21168 plots.

@@

Again, in principle this is correct, but in practice, no method exists to obtain accumulated local effects for SEM-forests. For the purpose of this paper, I developed a novel method to obtain marginal dependencies for growth curves, but I am not familiar with Apley's method so I cannot implement it (and either way, that seems out of scope for a developmental paper).

@@

@@

@@

@@

@@

@@

@@

@@

@@

\RC{Comments to the Author
The current study used machine learning to identify importance of predictors of adolescent emotion regulation trajectories. The study used a large sample of adolescents and included multiple reporters (although adolescent report was featured most heavily). Despite these strengths, I have a number of concerns about the manuscript in its present form that make its contribution unclear at this point. I list these concerns in roughly the order of appearance in the manuscript.}

@@

@@

@@

@@

@@

`r get_revision(man, "personcentered1")`

The second issue is whether our writing does sufficient justice to prior publications on predictors of emotion regulation.
We could not agree more with the Reviewer that there is a wealth of prior research in this area.
In fact, there is so much work on this topic that it would be a tall order to do it all justice.
We cite a recent (2021) comprehensive systematic review of 6305 studies on predictors of adolescent emotion regulation.
From those 6305 studies, we selected the ones that seemed most relevant for the present paper.
If the Reviewer feels that *specific* studies are missing here, we are happy to include them of course.
At the same time, we cannot strive to recreate a comprehensive review here. This also seems redundant, given that one was just recently published, and overly ambitious, given the page limits and attention that must be devoted to explaining the novel methods.
The present study builds upon prior reviews of the literature,
and those reviews are cited.

@@

`r get_revision(man, "abundantlit")`

@@

We respectfully believe that this may be an oversight on the Reviewer's part, as comprehensive descriptive statistics - including those requested by the reviewer - are reported in Tables 1 and 2.

@@

In the original manuscript, we stated that:

@@

As two Reviewers have requested this information, we understand that this is information readers will want to know. Note, however, that the methods we use are valid regardless of whether missingness is related to other variables in the dataset or not. To address this comment, we performed the suggested check, and report:

`r get_revision(man, "missing")`

@@

We thank the Reviewer for pointing out this unfortunate choice of words. 
Entropy is not a criterion for class enumeration, but for evaluating the quality of the chosen solution (see Jung \& Wickrama, 2008). In the Revision, we have attempted to clarify this as follows:

`r get_revision(man, "entropy")`

@@

In line with the Reviewer's expectation, we indeed used the median and 16th and 84th percentile. Percentiles do not assume a normal distribution of the predictor, and neither does the model, so this is a good fit. As we explain in the text, the 16th and 84th percentiles correspond to +/- 1SD of a standard normal distribution. We then use this label, "+/- 1SD", in the plots, in an attempt to make the results more understandable. Perhaps this was a misguided decision, but we were not sure whether the readership would be familiar with percentiles.

In the Revision, we have attempted to resolve this issue by stating:

`r get_revision(man, "percentiles")`

@@

REF

@@

We appreciate this point, and the writing here should certainly be more nuanced (that was an oversight).
We have rephrased this as follows:

`r get_revision(man, "riskassessment")`

@@

`r get_revision(man, "culture")`

>>>>

```{r, message=FALSE, warning=FALSE}
library(revise)
man <- read_manuscript("manuscript/manuscript.Rmd")
letter <- read_manuscript("action_letter.Rmd")
mask = TRUE
```

@@

Thank you for considering our manuscript for publication in _`r rmarkdown::metadata$journal`_.
We appreciate the thorough and critical comments you solicited,
which helped strengthen the argumentation, clarify the structure, and add nuance.
We have attempted to address all comments as thoroughly as possible.
All changes are explained below.
We hope that you will find the quality of the work to be sufficiently improved.

@@

@@

We completely agree with Reviewer 3 that there is already a wealth of prior research in this area.
In fact, there is so much work on this topic that it would be a tall order to review the literature on an individual study basis.
Given the large prior literature,
we rely primarily on prior review articles.
We currently cite 17 review articles in the introduction,
including a recent (2021) comprehensive systematic review of 6305 studies on factors associated with adolescent emotion regulation.

We cannot strive to recreate a comprehensive review here - 
and this also seems redundant, given that many of the cited review articles are very recent (i.e., from 2019-2021),
and seems overly ambitious, given the page limits and attention that must be devoted to explaining the novel methods,
and spurious, given that this is an exploratory study and thus has no hypotheses that must be supported with prior literature.
The present study builds upon prior reviews of the literature,
and those reviews are cited.

Of course we are willing to include specific omitted literature, but please note that Reviewer 3 does not mention which references they feel are missing.

`r get_revision(manuscript = man, "abundantlit")`

@@

As mentioned above, the vast majority of cited studies are reviews (narrative reviews, meta-analyses, and book chapters) or theoretical publications.
Although one would hope that such publications cover all available literature without selecting for country of origin,
some bias is likely present.
Of the few primary empirical studies we cited, all originated in the "Global North" (if one also considers Israel and Greece to be part of the Global North).
To address this comment, we have extracted information about the country of origin of the samples of all primary data sources cited.
This information is summarized in a new Supplemental Table,
which also indicates what references are *not* primary data sources but instead theoretical, review, or methodological articles.

To address this comment, we now state the following in the Limitations section:

`r get_revision(manuscript = man, "globalnorth")`

@@

To address this comment, we have incorporated the following in our analysis of the results in light of the bioecological model:

`r get_revision(manuscript = man, "velezagosto")`

@@

We respectfully believe that this may have been an oversight,
as the requested information was already provided. As per the submission guidelines, some specific details had been masked for review, which may have caused the confusion. To address this comment, we have unmasked these details in the revision:

@@

`r get_revision(manuscript = man, "waves")`

@@

`r get_revision(manuscript = man, "dutch")`

@@

`r get_revision(manuscript = letter, "extractpreds", quote = F)`

@@

<span id = "parents">We now realize that our imprecise use of language caused confusion about the relative importance of what we previously called "parenting" - by which we meant specific parenting practices.

In the revision, we have attempted to avoid confusion by distinguishing "parenting practices" from other "parent-related constructs".
Parenting practices are defined as specific parental actions related to child-rearing,
for example, support and dimensions of control [@petersonFamilySocialCompetence1990].
The highest-ranking parenting practice is parental control of friendships (16).

By contrast, parent-related constructs refer to any variable pertaining to a parent but that is not a parenting practice.
The highest ranking parent-related construct is balanced relatedness (3),
which measures whether the adolescent perceives his or her parents to be tolerant of the adolescent's differing beliefs.
Balanced relatedness is an aspect of the emotional family climate [@morrisRoleFamilyContext2007],
not a parenting practice, because it does not relate to specific parental actions.
The specific parenting practices associated with instilling a sense of balanced relatedness are maternal (54) and paternal (55) support, which rank very low.

The observation that *parenting practices* are relatively less important than individual predictors (and certainly much less important than we would have thought a-priori) is thus strongly supported by the data;
the first such behaviors are (16) and (25).
This is consistent with the finding that some parent-related constructs indeed score highly.

To address this comment, we have:

- Clarified the distinction between parenting practices and other parent-related constructs in the revision
- Used consistent terminology throughout 
- Provided a definition of parenting practices

We have rewritten the following paragraphs:

`r get_revision(manuscript = man, "parenting")`

And:

`r get_revision(manuscript = man, "parentrelated")`
</span>

@@

We thank the Editor for this excellent suggestion; we have addressed this comment by adding the following paragraph:

`r get_revision(manuscript = man, "velezagosto")`

@@

If we understand correctly, this is a statement and requires no further action.

@@

Reviewer 2 suggested that we include a Figure to illustrate the distribution of variable importances by level of the bioecological model and by theme, to illustrate the two ways we interpret the pattern of findings (see Figure 3).
We believe that this figure substantially clarifies our interpretation of the results.

```{r figviolin, results='asis', out.width="20%", fig.cap="Variable importances clustered by theme (A) and level of the bioecological model (B).", eval = FALSE}
knitr::include_graphics("violin.png")
```

Furthermore, to address the specific comment that "Predictors at the individual level were most important [etc]", we now refer to Figure 3 so readers can see the pattern we are describing.
At the same time, we now explicitly acknowledge that there is substantial overlap in importance of predictors at the different levels:

`r get_revision(manuscript = man, "overlap")`

@@

We thank the Reviewer for pointing this out. We have made the requested change.

@@

The performance of these fit statistics has been validated mostly in the context of cross-sectional data, and their performance is less well understood for longitudinal data.
This may affect the CFI more than, e.g., RMSEA, because CFI compares the fit of the theoretical model to a null model that may be less appropriate for repeated measures.
We now address this point in the revision:

`r get_revision(manuscript = man, "cfi")`

@@

We apologize; the Repository hosting these Supplementary Tables was still set to private at time of submission. This was intended to guarantee anonymous review. For this revision, it has been made public. The links now work.

@@

<span id = "missingness">To address this comment, and a comment by another Reviewer, we tested for differences on demographic characteristics and the dependent variable between participants with missing and complete data. We now mention this in the revised manuscript:

`r get_revision(manuscript = man, "missing")`
</span>

@@

We appreciate the Reviewer's kind words.
<span id = "extractpreds">
The method used to extract predictors is less groundbreaking than the Reviewer gives us credit for. PCA is the oldest dimension reduction technique (invented in 1901), and the main reason we use it here is because it makes fewer assumptions about the measurement model than, e.g., CFA.

We appreciate the Reviewer's excellent suggestion of providing a specific example to help readers understand this approach. To address this comment, we have thus made the following changes:

1. We added the requested illustrative example, using neuroticism. We could use any scale, but as Neuroticism later turns out to be the most important predictor, it seems a suitable candidate.
2. We have attempted to clarify our description of the dimension reduction procedure
3. We have added further statistics that, hopefully, give the reader a better sense of whether the use of these principal components is defensible. Specifically, we no longer just provide the explained variance by each first component - but we also standardize this explained variance by the number of items in the scale to see how much more variance the first component explains than expected by chance. We see that, across all scales, the first component explains between 1.6 - 17.46 times more variance than expected by chance.
</span>

@@

`r get_revision(manuscript = man, "homogeneity")`

@@

`r get_revision(manuscript = man, "homogeneity2")`

@@

We have rewritten this step in an attempt to address this comment. It now reads:

`r get_revision(manuscript = man, "stepiii")`

@@

`r get_revision(manuscript = man, "fullygrown")`

@@

`r get_revision(manuscript = man, "semforests")`

@@

`r get_revision(manuscript = man, "predictions")`

@@

`r get_revision(manuscript = man, "examplenonlinear")`

@@

`r get_revision(manuscript = man, "limitations")`

@@

Thank you for this suggestion; we agree that many people would be interested in such an overview. One major caution is that such post-hoc analyses should not be over-interpreted; they are in no way a substitute for the (much more flexible) machine learning models. Still, we see that having an overview of univariate linear effects might be useful, for example, to determine expected effect sizes if people want to take guidance from our list of important predictors to help plan follow-up studies.

To address this comment, we have therefore added the following paragraph and an additional Supplemental Table:

`r get_revision(manuscript = man, "posthoc")`

@@

`r get_revision(manuscript = man, "errata")`

@@

`r get_revision(manuscript = man, "includepersonality")`

@@

This is correct; at the time of submission, the repository on GitHub was still set to private to safeguard blind review. For the revision, this has been resolved.

@@

We apologize for the inconvenience. The manuscript only has 42 pages; pages 43-65 are copies of the online supplemental materials (which are supposed to be accessed via the broken links, which have now been fixed). For the sake of blind review, we also submitted copies of these tables through the submission portal, but it evidently cannot correctly present these materials. The tables will not be part of the paper in this form.

@@

We thank the Reviewer for their kind words and thoughtful comments, which have been instrumental in improving the manuscript.
Please see our detailed responses to the specific comments below.

@@

Model tuning and cross-validation are indeed industry standard procedures in machine learning.
However, these methods do not (yet?) exist for SEM-forests.
This is because there is no single error metric for SEM-forests that can be optimized.
For standard random forests, this error metric is the root mean squared error (difference between predicted and observed values for all cases).
The "outcome" of each regression tree in the SEM-forest is an entire SEM-model, for which there is no clear-cut case-specific error metric.
It is important to note, however, that unlike other machine learning techniques, random forests typically achieve competitive performance even with default settings [@probstHyperparametersTuningStrategies2019].
Thus, even when a random forest isn't tuned - or cannot be tuned, as is the case here - it should perform well.
Although we did attempt to explain these points in the previous version of the manuscript,
we have attempted to address this comment by further emphasizing this in the Revision:

`r get_revision(manuscript = man, "limitations")`

@@

We thank the Reviewer for this excellent suggestion, and have now included a new Figure (Figure 3) that clusters variable importances by (inductive) theme as discussed in the results section, as well as by level of the bioecological model.
We now refer to this Figure when discussing the relative importance of each theme / level.

```{r}
knitr::include_graphics("violin.png")
```

@@

We thank the Reviewer for pointing out the apparent inconsistency between the conclusion and results.

`r get_revision(manuscript = letter, "parents", quote = F)`

We also believe that the Figure above helps clarify these results.

@@

We agree with the Reviewer that is is prudent to caution against undue causal interpretation of the results - which we have done in the Limitations section:

`r get_revision(manuscript = man, "causality")`

We do believe that the quoted statement is correct and does not require further modification, however, as it does not relate to causal interpretation of the results, but to the affordances of the method: latent class analysis *cannot* answer the question "Why?" some adolescents follow similar causal trajectories,
whereas SEM-forests *can* answer this question, because cases are clustered based on predictor variables (of course with the caveat that causal interpretation is contingent on study design or theoretical justification).

@@

We appreciate the suggestion and had considered a similar approach - but it is not practically feasible for the following reasons:

1. Computing univariate partial dependence profiles is extremely computationally expensive; bivariate partial dependence is prohibitively so.
2. There is no a-priori way to determine which bivariate interactions might be important in SEM-forests analysis (because there is no applicable analogy for Friedman's H statistic).
3. Consequently, one would have to examine all bivariate interactions by hand. This comes down to interpreting 84*84*3 = 21168 plots. This is not possible.

With this in mind, we think it would be preferable *not* to muddy the waters by citing literature on interaction effects for random forests; not until suitable methods have been developed for SEM-forests as well.

@@

Again, we thank the Reviewer for the suggestion;
in principle this is correct, but in practice, no method (currently?) exists to obtain accumulated local effects for SEM-forests.
The Reviewer is citing cutting-edge developments in the area of classic random forests; it will take a while before these developments spill over into the SEM-forests literature, if ever.

@@

We respectfully believe that this may be an oversight on the Reviewer's part, because the manuscript says:

`r get_revision(manuscript = man, "singlefactor")`

We do not believe further action is required on this point - but if we missed something, please let us know.

@@

The performance of these fit statistics has been validated mostly in the context of cross-sectional data, and their performance is less well understood for longitudinal data.
This may affect the CFI more than, e.g., RMSEA, because CFI compares the fit of the theoretical model to a null model that may be less appropriate for repeated measures.
We now address this point in the revision:

`r get_revision(manuscript = man, "cfi")`

@@

We apologize for the oversight; the y-axis was indeed reversed in this Figure. We have corrected this mistake.

@@

We assumed homoscedastic residuals because otherwise the model would be too complex to estimate. We would have more parameters for the residuals than for the rest of the model, and the SEM-forest analysis would thus be primarily driven to explain differences in residuals, instead of in growth curves.

A SEM-forest method estimates tens, or hundreds of thousands of SEM models in its different nodes. It is not possible to test model assumptions in each of those nodes.
This applies not only to the assumption of homogeneity of residuals, but to all other assumptions, for example, about normality of residuals, or the shape of the growth trajectories.

`r get_revision(manuscript = man, "homogeneity")`

`r get_revision(manuscript = man, "homogeneity2")`

@@

We have corrected this mistake.

@@

We thank the Reviewer for the suggestion,
and defer to the Editor on this point.

@@

We have clarified this by writing:

`r get_revision(manuscript = man, "motherfather")`

@@

We apologize for the inconvenience. These Supplemental Tables will not be part of the printed manuscript; we were required to attach hard copies of the online supplemental tables in the submission portal, and these were evidently not formatted correctly. They are just spreadsheets that can be opened in a web-browser or excel.

@@

@@

We appreciate these suggestions and the caution about abstract length; we have cut the abstract by half and attempted to incorporate the Reviewer's suggestions. The Abstract now reads:

`r get_revision(manuscript = man, "abstract")`

@@

The statement is a continuation of the preceding sentence,
which is supported by two references. 
To address this comment, we now also added one of these references to the second sentence, and emphasize the connection between the sentences by re-iterating that the societal cost is incurred via emotion regulation-related mental health problems:

`r get_revision("cost", man)`

@@

We agree with the Reviewer that the word "destinies" has unintended connotations of fixedness in developmental outcomes.
We certainly want to avoid this implication, and have rephrased all occurrences of "diverging destinies" with "diverging trajectories", which is a statistically accurate description of our outcome of interest.

@@

We have attempted to correct all such errors.

@@

`r get_revision(manuscript = man, "personcentered1")`

The second issue is whether our writing does sufficient justice to prior publications on predictors of emotion regulation.
We could not agree more with the Reviewer that there is a wealth of prior research in this area.
In fact, there is so much work on this topic that it would be a tall order to do it all justice.
At present, we cite a total of 17 review articles in the introduction,
including a recent (2021) comprehensive systematic review of 6305 studies on factors associated with adolescent emotion regulation.

Given the large prior literature,
we found it necessary to rely primarily on review articles to do justice to prior work.
We cannot strive to recreate a comprehensive review here - 
and this also seems redundant, given that many of the cited review articles are very recent (i.e., from 2019-2021),
and seems overly ambitious, given the page limits and attention that must be devoted to explaining the novel methods,
and spurious, given that this is an exploratory study and thus has no hypotheses that must be supported with prior literature.
The present study builds upon prior reviews of the literature,
and those reviews are cited.

Of course we are willing to include **specific** omitted literature, but it is not clear from the comment which specific references should be included.

@@

`r get_revision(manuscript = man, "abundantlit")`

@@

Comprehensive descriptive statistics about all available demographic characteristics are reported in Tables 1 and 2.
To address this comment, we now stress this in the Participants section:

`r get_revision("demographics", man)`

@@

We respectfully believe that this may be an oversight on the Reviewer's part, as the original manuscript stated that:

@@

`r get_revision("missingness", letter, quote = F)`

Note, however, that the methods we use are valid regardless of whether missingness is related to other variables in the dataset or not (i.e., valid for MCAR and MAR).

@@

We thank the Reviewer for pointing out this unfortunate choice of words, which should have been flagged during proof reading.
Entropy is not a criterion for class enumeration, but for evaluating the quality of the chosen solution (see Jung \& Wickrama, 2008). In the Revision, we have attempted to clarify this as follows:

`r get_revision(manuscript = man, "entropy")`

@@

In line with the Reviewer's expectation, we did in fact use the median and 16th and 84th percentile.
The confusion arises from our attempt to explain to the readership what these percentiles mean, by drawing a comparison to +/- 1SD.

We use percentiles is because they do not assume a normal distribution of the predictor, and neither does the model, so this is a good fit.
As we explain in the text, the 16th and 84th percentiles and the median correspond to +/- 1SD and the mean of a standard normal distribution.
We then use the labels "+/- 1SD" in the plots, in an attempt to make the results more understandable, and explain that these correspond to percentiles of a normal distribution in the text.

In the Revision, we have attempted to address this issue by further clarifying that :

`r get_revision(manuscript = man, "percentiles")`

@@

`r get_revision(manuscript = letter, "parents", quote = F)`

To address this comment, we now also mention highly ranked parent-related constructs in the first paragraph of the Discussion:

`r get_revision(manuscript = man, "highrankingparent", quote = F)`

@@

This is a fair point, and the writing here should have been much more nuanced (that was an oversight).
We have rephrased this as follows:

`r get_revision(manuscript = man, "riskassessment")`

@@

`r get_revision(manuscript = man, "culture")`

And also about cultural bias in prior literature:

`r get_revision(manuscript = man, "globalnorth")`
